%Copyright 2013-2014, 2023 Steph Kraemer

\documentclass{letter}

\usepackage[colorlinks=true, urlcolor=blue]{hyperref}
\usepackage{grffile}
\usepackage{geometry}

\usepackage{titlesec}

% Set font for section headings
\titleformat{\section}
{\Large\bfseries\sffamily}{\thesection}{1em}{}

% Set font for subsection headings
\titleformat{\subsection}
{\large\bfseries\sffamily}{\thesubsection}{1em}{}

% Set font for subsubsection headings
\titleformat{\subsubsection}
{\normalfont\bfseries\sffamily}{\thesubsubsection}{1em}{}

%margins
\newgeometry{left=20mm,right=20mm,top=10mm, bottom=20mm}

%get rid of headers/footers (i.e. no page numbers)
\pagestyle{empty}

\begin{document}

<<<<<<< HEAD
{\Huge\bf Steph Kraemer} \hfill
=======
{\Huge\bf Steph Kraemer} (they/she) \hfill
>>>>>>> 9b0c6e7 (update resume)
\begin{tabular}{r}
  \href{mailto:purple.stephyr@fmgirl.com}{purple.stephyr@fmgirl.com} \\
  <phone number goes here> \\
  \href{https://www.linkedin.com/in/steph-kraemer/}{https://www.linkedin.com/in/steph-kraemer/}
\end{tabular}

%horizontal line
\vskip 2pt
\hrule

{\large\bf SUMMARY} \\
I am a highly skilled software developer with 9 years professional experience. I have expertise in systems programming, networking (especially L2/EVPN control-plane), and unit-testing. I take pride in my ability to write high-quality code and focus on thorough unit testing to ensure the reliability and performance of my software. With a proven track record of productivity and attention to detail, I bring a strong work ethic and a passion for programming to every project I work on.
\vskip 2pt

{\bf Technical Skills}

\begin{itemize}
  \item Programming Languages: C/C++, Python
  \item Network Protocols: EVPN, L2VPN, MPLS, Segment Routing (SRv6), NETCONF/YANG
  \item Operating Systems: Linux (Arch, Ubuntu, RHEL)
  \item Tools: gdb, valgrind, git, svn, make, jam, LaTeX, emacs
\end{itemize}

%horizontal line
\vskip 2pt
\hrule
{\large\bf PROFESSIONAL EXPERIENCE}

{\bf Cisco,} IOS-XR L2VPN/EVPN Team, {\sl Ottawa, ON} \hfill July 2014 - Present \\
{\sl Software Developer} \\ \\
Responsibilities:
\begin{itemize}
  \item Develop and maintain features for L2VPN/EVPN protocols on IOS-XR platform.
  \item Implement complex features for high-availability scenarios with focus on quality and performance.
  \item Design and review architectural changes to improve system scalability and stability.
  \item Automate unit-testing and integration testing to ensure software quality.
\end{itemize}
Acheivements:
\begin{itemize}
  \item Implemented features including Flexible-Cross-Connect-Service, EVPN-Tree, On-Demand-Nexthop.
  \item Fixed hundreds of baseline unit-test failures, stabilizing unit tests to be usable as a precommit gate.
  \item Found and fixed many memory issues, and enabled valgrind and ASAN testing as a precommit gate.
  \item Optimized unit test process, bringing runtime down from over 1 hour to under 5 minutes
\end{itemize}
%horizontal line
\vskip 2pt
\hrule
{\large\bf EDUCATION}

{\bf Bachelor of Applied Science} \hfill Sept 2009 - Apr 2014 \\
Honours Mechatronics Engineering, Co-operative Program (With Distiction) \hfill University of Waterloo, ON
\begin{itemize}
  \item 3.5 GPA
\end{itemize}

{\bf Fourth Year Design Project} - ``Smart'' Luggage \hfill Sept 2013 - Apr 2014
\begin{itemize}
  \item Designed a ``smart'' suitcase that collects various data from sensors, displaying it in an app.
  \item Software lead in a team of four, coded in C++, Java, PHP, using an Arduino and creating an app on Android.
\end{itemize}

{\bf Co-op Positions} \hfill Sept 2010 - Dec 2013
\begin{itemize}
  \item Oracle, Endeca Server Team - Software Developer \hfill Apr-Aug 2013
  \item Autodesk, Alias Team - Software Developer \hfill Aug-Dec 2012
  \item Avvasi Inc, Packet Processing Team - Software Developer \hfill Jan-Apr 2012
  \item Netkeepers - Support Technician \hfill May-Aug 2011
  \item University of Waterloo - Teaching Assistant \hfill Jan-Apr,Sep-Dec 2010
\end{itemize}

\end{document}
